[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-29 README/getting_started_guide.tex
Minor refactoring

Load a Docker image by running
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
\end{verbatim}
%
It creates an image named \texttt{hybrid\_aara} and stores it locally on your
%
Docker may create an image with a slightly different name from
\texttt{hybrid\_aara}.
%
You can check the name of the image by running \verb|$ docker images|, which
will display a list of images on your local machine.

To run the image \texttt{hybrid\_aara}, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
%
It creates a Docker container (i.e., a runnable instance of the Docker image)
named \texttt{hybrid\_aara} and starts a shell inside the container.

>>>>

Load a Docker image by running
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
\end{verbatim}
%
It creates an image named \texttt{hybrid\_aara} and stores it locally on your
%
Docker may create an image with a slightly different name from
\texttt{hybrid\_aara}.
%
To check the name of the image, display all Docker images on your local machine
by running
\begin{verbatim}
$ docker images
\end{verbatim}

To run the image \texttt{hybrid\_aara}, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
%
It creates a Docker container (i.e., a runnable instance of the Docker image)
named \texttt{hybrid\_aara} and starts a shell inside the container.
%
If the command does not run properly, you can instead build the image locally on
your machine as instructed in \cref{sec:Build the Docker Image}.
